Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-23 Paper/Paper.tex
improved

Then, we use the LLE\footnote{implementation:
  \url{http://www.astro.washington.edu/users/vanderplas/coding/LLE/}}
algorithm \cite{Roweis2000} to visualize codewords arranged in
coherent groups (Figure \ref{fig:lle}).

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes1}
\end{center}
\caption{\small{
Most used codes in the codebook in term of frequency of use in the test
set (artist20, see Subsection \ref{ssec:artist}). 
This codebook was of size $200$ and trained on $2$ bars, pattern
size is $12$x$8$. Code in Figure \ref{fig:code} is the $8$th most used
here (second row, third column). 
Numbers display are the index (from most used to least) and in parentheses
the percentage of use in the whole collection times.
There is $71832$ patterns in total in the dataset.
}}
\label{fig:codes1}
\end{figure}

>>>>

\begin{figure}[h]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes1}
\end{center}
\caption{\small{
Most used codes in the codebook in term of frequency of use in the test
set (artist20, see Subsection \ref{ssec:artist}). 
This codebook was of size $200$ and trained on $2$ bars, pattern
size is $12$x$8$. Code in Figure \ref{fig:code} is the $8$th most used
here (second row, third column). 
Numbers display are the index (from most used to least) and in parentheses
the percentage of use in the whole collection times.
There is $71832$ patterns in total in the dataset.
}}
\label{fig:codes1}
\end{figure}

Another interesting visualization uses LLE\footnote{implementation:
  \url{http://www.astro.washington.edu/users/vanderplas/coding/LLE/}}
algorithm \cite{Roweis2000} to display codewords arranged in
coherent groups. See Figure \ref{fig:lle}.

@@
